Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
add  ref to section stand and eraly/late int

\subsection{Early \vs late temporal integration}
Owing to the scarcity of salient events in many natural scenes,
fine-grained classification is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate two classes auditory scenes which share part of their semantic content, \eg a train from a subway station or a quiet street from a park.
Depending on whether aggregation is performed in feature space or in decision space, the corresponding method is referred to as early or late integration.

@@

\subsection{Standardization}
Let $\mathbf{S}\boldsymbol{X}(\gamma,n)$ be a dataset, where the indices $\gamma$ and $n$ respectively denotes features and examples.
It is commonly acknowledged that support vector machines should be trained on scaled features with null mean and unit variance, so as to avoid mismatch in numeric ranges.
This operation may also help making the dataset linearly separable in feature space.
To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we apply the affine transformation
\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma)}{\sigma[ \mathbf{S}\boldsymbol{X}](\gamma)}
\end{equation}
where $\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma) = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the expected value of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma[\mathbf{S}\boldsymbol{X}] (\gamma) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mathbb{E}[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
 is the sample standard deviation.

@@

To take into account this object-based representation, we propose the following 3-steps algorithm:

@@

The \emph{ob} approach is compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASS setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{XX}).

@@

As most of the 2013 DCASE challenge participant did, a Support Vector Machine (SVM), which is a large-margin binary discriminators with tunable regularization of misclassified examples, is used as classifier for the ASC setting. For the \emph{ob} approach, we use XX. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approach, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All features, that is the frames, the pooled frames or the centroids depending on the approach considered, are standardized prior to be filled into the classifier. The standardization is computed with respect to the train/test set split of the cross validation scheme (see \ref{}).

>>>>

\subsection{Early \vs late temporal integration}
\label{sec:eili}

Owing to the scarcity of salient events in many natural scenes,
fine-grained classification is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate two classes auditory scenes which share part of their semantic content, \eg a train from a subway station or a quiet street from a park.
Depending on whether aggregation is performed in feature space or in decision space, the corresponding method is referred to as early or late integration.

@@

\subsection{Standardization}
\label{sec:stand}

Let $\mathbf{S}\boldsymbol{X}(\gamma,n)$ be a dataset, where the indices $\gamma$ and $n$ respectively denotes features and examples.
It is commonly acknowledged that support vector machines should be trained on scaled features with null mean and unit variance, so as to avoid mismatch in numeric ranges.
This operation may also help making the dataset linearly separable in feature space.
To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we apply the affine transformation
\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma)}{\sigma[ \mathbf{S}\boldsymbol{X}](\gamma)}
\end{equation}
where $\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma) = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the expected value of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma[\mathbf{S}\boldsymbol{X}] (\gamma) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mathbb{E}[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
 is the sample standard deviation.

@@

To take into account this object-based representation, we propose the following 4-steps algorithm:

@@

The \emph{ob} approach is compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASS setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{sec:eili}).

@@

As most of the 2013 DCASE challenge participant did, a Support Vector Machine (SVM), which is a large-margin binary discriminators with tunable regularization of misclassified examples, is used as classifier for the ASC setting. For the \emph{ob} approach, we use XX. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approach, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All features, that is the frames, the pooled frames or the centroids depending on the approach considered, are standardized prior to be filled into the classifier. The standardization is computed with respect to the train/test set split of the cross validation scheme (see \ref{sec:stand}).
